Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-20 manuscript_covid19dashboard.Rmd
Updated

>>>>

## Data

We obtained data from COVID-19 situation reports published by Epidemiology Unit, Ministry of Health Sri Lanka. We obtained data corresponds to number of death cases, number of reported cases, number of recovered cases and COVID-19 vaccinated counts in Sri Lanka. The data are made available through an open-source R package covid19srilanka [@talagala].

## Software

R software was used for data cleaning and analysis. The flexdashboard [@flexdashboard] package was used to build the data visualization dashboard.

## Data visualization

Inorder, to compare patterns across districts min-max transformation is used to normalize data into 0-1 scale.

### 2022-04-20 manuscript_covid19dashboard.tex
Updated

@@

@@

>>>>

\hypertarget{data}{%
\subsection{Data}\label{data}}

We obtained data from COVID-19 situation reports published by
Epidemiology Unit, Ministry of Health Sri Lanka. We obtained data
corresponds to number of death cases, number of reported cases, number
of recovered cases and COVID-19 vaccinated counts in Sri Lanka. The data
are made available through an open-source R package covid19srilanka
(Talagala 2021).

\hypertarget{software}{%
\subsection{Software}\label{software}}

R software was used for data cleaning and analysis. The flexdashboard
(Iannone, Allaire, and Borges 2020) package was used to build the data
visualization dashboard.

\hypertarget{data-visualization}{%
\subsection{Data visualization}\label{data-visualization}}

Inorder, to compare patterns across districts min-max transformation is
used to normalize data into 0-1 scale.

@@

\leavevmode\hypertarget{ref-flexdashboard}{}%
Iannone, Richard, JJ Allaire, and Barbara Borges. 2020.
\emph{Flexdashboard: R Markdown Format for Flexible Dashboards}.
\url{https://CRAN.R-project.org/package=flexdashboard}.

@@

\leavevmode\hypertarget{ref-talagala}{}%
Talagala, Thiyanga S. 2021. \emph{Covid19srilanka: The 2019 Novel
Coronavirus COVID-19 (2019-nCoV) Data in Sri Lanka}.
\url{https://github.com/thiyangt/covid19srilanka}.
